---
title: "Kaggle Survey Cleaning - Project 3"
author: "Jeff Shamp"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: vignette
---

# Kaggle DS survery 2019 - Clean and Write to DB

This file is load the Kaggle Data Science Survey for 2019, cleans it, divides the questions into subsets, and writes the subsets to our project SQL server. 

```{r, include=FALSE}
library(tidyr)
library(dplyr)
library(dbplyr)
library(ggplot2)
library(RCurl)
library(RMySQL)
library(stringr)
```


Below is the bulk data file. We don't know to drag around all the data all the time so I'm going to split this dataframe up into subsets and clean them up for easy tidying downstream. 

```{r}
file<-"/Users/jeffshamp/Documents/GitHub/cuny_msds/DATA_607/data/multiple_choice_responses.csv"
df<-read.csv(file = file,sep = ",", stringsAsFactors = F, na.strings =T)%>% 
  mutate_if(is.character, list(~na_if(.,""))) 
```

The first table we want is the basic information; age, country, education level, company size, salary, experience level, etc. 

```{r}
df_basic<- df %>%
  select(Q1:Q2,Q3:Q4,Q6:Q8, Q10,Q11,Q15) %>%
  rename(age = Q1,         # custom name for columns
         gender = Q2, 
         country = Q3,
         education = Q4,
         company_size = Q6,
         ds_team_size = Q7,
         company_use_ml = Q8,
         compensation_USD = Q10,
         spend_ml_cloud_work_USD = Q11,
         code_exp_years = Q15) %>%
  slice(2:(dim(df)[1])) %>%
  mutate(                  # Following mutatations to clean formatting
    country = str_replace_all(country,
                "United Kingdom of Great Britain and Northern Ireland",
                "United Kingdom")) %>%
  mutate(company_size = str_remove_all(company_size, "employees")) %>%
  mutate(education = str_remove_all(education, "degree")) %>%
  mutate(education = str_remove_all(education, "[:punct:]")) %>%
  mutate(compensation_USD = str_remove_all(compensation_USD, "[$]")) %>%
  mutate(spend_ml_cloud_work_USD = str_remove_all(spend_ml_cloud_work_USD,"[$]")) %>%
  mutate(spend_ml_cloud_work_USD = str_remove_all(spend_ml_cloud_work_USD,"\\(USD\\)")) %>%
  mutate(code_exp_years= str_remove_all(code_exp_years, "years")) %>%
  mutate(code_exp_years= str_replace_all(code_exp_years, "I have never written code", "None"))
df_basic
```

A lot of columns end with a technology or choice so i'll rename the columns based the row selection choice. Also cleaning the column names to standard format. 

```{r}
rename.columns<- function(df){
items<- rep(NA, dim(df)[2])
for (i in 1:ncol(df)){
  items[i]<- str_extract(df[1,i], "[-].*")
  items[i]<- str_remove(items[i], "- Selected Choice -  |- Selected Choice -")
  items[i]<- str_remove(items[i], "\\(.*\\)")
  items[i]<- str_replace(items[i], "[:punct:]\\s", "")
  items[i]<- str_remove_all(items[i], "\\s$|^\\s")
  items[i]<- str_replace_all(items[i], "\\s", "_")
  items[i]<- str_remove(items[i], "_$")
  names(df)[names(df) == names(df[i])]<-items[i]
}
df<- df %>% slice(2:dim(df)[1])
return(df)
}
```

Rip throught the subsets for cleaning.

```{r}
# Primary Tool for DA at school/work
df_prime_tool<- df %>% 
  select(Q14 )%>%
  slice(2:dim(df)[1]) %>%
  rename(primary_analysis_tool = Q14)
# ML year EXP
df_ml_xp<- df %>% select(Q23) %>%
  slice(2:dim(df)[1]) %>%
  rename(ml_exp_years = Q23) %>%
  mutate(ml_exp_years = str_remove_all(ml_exp_years, "years"))
# language to learn first?
df_lang_rec<- df%>% 
  select(Q19) %>%
  slice(1:dim(df)[1]) %>%
  rename(rec_lang = Q19)
#media sources for DS
df_media<- df %>% select(Q12_Part_1:Q12_Part_12) %>%
  slice(2:dim(df)[1]) %>%
  rename(twiter = Q12_Part_1,
         hacker_news = Q12_Part_2,
         reddit = Q12_Part_3,
         kaggle = Q12_Part_4,
         course_forums = Q12_Part_5,
         you_tube = Q12_Part_6,
         podcast = Q12_Part_7,
         blogs = Q12_Part_8,
         journals = Q12_Part_9,
         slack_communities = Q12_Part_10,
         none = Q12_Part_11,
         other = Q12_Part_12)
# DS course work including University
df_online_ed<- df %>% 
  select(Q13_Part_1:Q13_Part_12) 
df_online_ed<- rename.columns(df_online_ed) 
# IDE
df_ide <- df %>% 
  select(Q16_Part_1:Q16_Part_12) 
df_ide<-rename.columns(df_ide)
# language
df_lang<- df %>%
  select(Q18_Part_1:Q18_Part_12) 
df_lang<- rename.columns(df_lang)
# data viz
df_viz <- df %>% 
  select(Q20_Part_1:Q20_Part_12) 
df_viz<- rename.columns(df_viz) 
# ML algo used regualrly
df_ml_algo<- df %>%select(Q24_Part_1:Q24_Part_12) 
df_ml_algo<-rename.columns(df_ml_algo)
# ML Tools (e.g. AutoML)
df_ml_tool<- df %>% select(Q25_Part_1:Q25_Part_8) 
df_ml_tool<- rename.columns(df_ml_tool) 
# CV tools
df_cv<- df %>% select(Q26_Part_1:Q26_Part_7)
df_cv<-rename.columns(df_cv)
# NLP tools
df_nlp<- df %>% select(Q27_Part_1:Q27_Part_6)
df_nlp<- rename.columns(df_nlp)
# Cloud platform
df_cloud<- df %>% select(Q29_Part_1:Q29_Part_12)
df_cloud<- rename.columns(df_cloud)
# cloud products
df_cloud_prod<- df %>% select(Q30_Part_1:Q30_Part_12)
df_cloud_prod<- rename.columns(df_cloud_prod)
# big data platform
df_big_data<- df %>%select(Q31_Part_1:Q31_Part_12)
df_big_data<- rename.columns(df_big_data)
# cloud ML (e.g. Sagemaker)
df_cloud_ml<- df %>% select(Q32_Part_1:Q32_Part_12)
df_cloud_ml<- rename.columns(df_cloud_ml)
# relational DB
df_db<- df %>% select(Q34_Part_1:Q34_Part_12)
df_db<- rename.columns(df_db)
```



```{r}
df_basic %>%
  ggplot() + 
  geom_bar(aes(x=age),fill="lightblue")
```

```{r}
df_basic
```

```{r}

```


```{r}
df_basic %>%
  filter(country=="United States of America" & compensation_USD != "NA") %>%
  ggplot() + 
  geom_bar(aes(x=compensation_USD),fill="lightblue") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```





