---
title: "LQ Scraping"
author: "Layla Quinones"
date: "3/14/2020"
output: html_document
---

```{r setup, include=FALSE, warning = FALSE, hide = TRUE}
library(rvest)
library(stringi)
library(tidyverse)
library(RCurl)
library(rebus)     
library(lubridate)
library(xml2)
library(kableExtra)
```

> Note: Scroll all the way down to the DATA section to see all the tables this code renders. It's long.

# Web Scraping for Key Words
APPROACH: Web scrape to create various websites and save a list of key words that pertain to Data Science skills.
```{r}
# Website with html table in link
url <- "https://en.wikipedia.org/wiki/Data_science"

#Parse
url <- read_html(url)

#Reads selecters from css
htmlData <- html_nodes(url, ".vertical-navbox") %>%
  html_text()

#RegEx
cleanData <- unlist(str_extract_all(htmlData, "[A-Za-z]+.*\\n+"))
wordList <- unlist(str_remove_all(cleanData, "\\n"))
wordList <- unlist(str_remove_all(wordList, "\\..*"))
wordList <- unlist(str_remove_all(wordList, "and"))
wordList <- wordList[1:87]
```

```{r}
#KD Nuggets Data
urlTwo<- "https://www.kdnuggets.com/2019/04/top-data-science-machine-learning-methods-2018-2019.html"

#Parse
urlTwo <- read_html(urlTwo)

#Reads selecters from css
htmlDataTwoA <- html_nodes(urlTwo, ".three_ul") %>%
  html_text()

#RegEx
cleanDataTwo <- unlist(str_extract_all(htmlDataTwoA, "[A-Za-z]+.*\\n+"))
cleanDataTwo <- unlist(str_remove_all(cleanDataTwo, "\\d+.*"))
cleanDataTwo <- unlist(strsplit(cleanDataTwo, ","))
cleanDataTwo  <- unlist(str_split(cleanDataTwo , "\\("))
cleanDataTwo  <- unlist(str_remove_all(cleanDataTwo, "/"))
cleanDataTwo  <- unlist(str_remove_all(cleanDataTwo, "\\)"))
cleanDataTwo  <- unlist(str_remove_all(cleanDataTwo, "-*"))
cleanDataTwo  <- unlist(str_remove_all(cleanDataTwo, "\\n"))
cleanDataTwo  <- unlist(str_remove_all(cleanDataTwo, "\\n"))
cleanDataTwo <- cleanDataTwo[1:19]

#Add to our initial word list
wordList <- c(wordList, cleanDataTwo)

#Part 2 (seperate selector)
htmlDataTwoB <- html_nodes(urlTwo, "ul") %>%
  html_text()

#RegEx
htmlDataTwoB <- c(htmlDataTwoB[2], htmlDataTwoB[3])
htmlDataTwoB <- unlist(str_extract_all(htmlDataTwoB, ".*\\n"))
htmlDataTwoB <- unlist(str_remove_all(htmlDataTwoB, "\\n+"))
htmlDataTwoB <- unlist(str_extract_all(htmlDataTwoB, ".*,+?"))
htmlDataTwoB <- unlist(str_remove_all(htmlDataTwoB, ",.*"))
htmlDataTwoB <- unlist(str_remove_all(htmlDataTwoB, "\\sand\\s"))
htmlDataTwoB <- unlist(str_remove_all(htmlDataTwoB, "&"))
htmlDataTwoB <- unlist(str_remove_all(htmlDataTwoB, "-.*"))
htmlDataTwoB <- unlist(str_split(htmlDataTwoB, "\\("))
htmlDataTwoB <- unlist(str_remove_all(htmlDataTwoB, "\\)"))
htmlDataTwoB <- unlist(str_remove_all(htmlDataTwoB, "/"))

#Add to our initial word list
wordList <- c(wordList, htmlDataTwoB)
```

```{r}
# Utica MS
urlThree <- "https://landing.online.utica.edu/msds-af?utm_source=banshee&utm_campaign=discoverdatascience&utm_content=mds&utm_term=datascience&viq_channel=af"

#Parse
urlThree <- read_html(urlThree)

#Reads the table in the html page (within "class selector")
uticaData <- html_nodes(urlThree, "ul") %>%
  html_text() 

uticaData <- unlist(str_extract_all(uticaData, ".*\\n"))
uticaData <- unlist(str_remove_all(uticaData, "\\n*\\t*"))
uticaData <- unlist(str_remove_all(uticaData, ":+.*"))

#Add to our initial word list
wordList <- c(wordList, uticaData)
```

```{r}
#  Saint Marys MS
urlFour <- "https://landing.onlineprograms.smumn.edu/msbida-af?utm_source=banshee&utm_campaign=discoverdatascience&utm_content=mds&utm_term=datascience&viq_channel=af"

#Parse
urlFour <- read_html(urlFour)

#Reads the table in the html page (within "class selector")
maryData <- html_nodes(urlFour, "li") %>%
  html_text() 


#Add to our initial word list
wordList <- c(wordList, maryData)
```


```{r}
#  US Bureau of Labor Stats
urlFive <- "https://www.bls.gov/ooh/computer-and-information-technology/computer-and-information-research-scientists.htm#tab-4"

#Parse
urlFive <- read_html(urlFive)

#Reads the table in the html page (within "class selector")
laborData <- html_nodes(urlFive, "strong") %>%
  html_text() %>%
  .[4:13]

laborData <- unlist(str_remove_all(laborData, "\\."))
#Add to our initial word list
wordList <- c(wordList, laborData)
```

```{r}
#  US Bureau of Labor Stats
urlSix <- "https://www.bls.gov/ooh/math/operations-research-analysts.htm#tab-4"

#Parse
urlSix <- read_html(urlSix)

#Reads the table in the html page (within "class selector")
laborDataTwo <- html_nodes(urlSix, "strong") %>%
  html_text() %>%
  .[4:13]

laborDataTwo <- unlist(str_remove_all(laborDataTwo, "\\."))
#Add to our initial word list
wordList <- c(wordList, laborDataTwo)
```

```{r}
# Edureka Article
urlSeven <- "https://www.edureka.co/blog/data-scientist-skills/"

#Parse
urlSeven <- read_html(urlSeven)

#Reads the table in the html page (within "class selector")
eurekaData <- html_nodes(urlSeven, "ul li span") %>%
  html_text() %>%
  .[7:17]
eurekaData <- unlist(str_remove_all(eurekaData, "\\sand\\s"))
eurekaData <- unlist(str_remove_all(eurekaData, "At least one programming language – "))
eurekaData <- unlist(strsplit(eurekaData, "/"))
eurekaData <- unlist(strsplit(eurekaData, ","))
eurekaData <- unlist(str_remove_all(eurekaData, "^[ \t]+")) %>% .[-14]

#Add to our initial word list
wordList <- c(wordList, eurekaData)
```

```{r}
# Edureka Article
urlEight <- "https://www.edureka.co/blog/how-to-become-a-data-scientist/"

#Parse
urlEight <- read_html(urlEight)

#Reads the table in the html page (within "class selector")
eurekaDataTwoA <- html_nodes(urlEight, "ol li span") %>%
  html_text() 

eurekaDataTwoB <- html_nodes(urlEight, "ul li span") %>%
  html_text() %>%
  .[8:50] 

eurekaDataTwoB <- unlist(str_split(eurekaDataTwoB, "\\(.*"))
eurekaDataTwoB <- unlist(stri_remove_empty(eurekaDataTwoB))
eurekaDataTwoB <- unlist(str_split(eurekaDataTwoB, "\\sand\\s"))
eurekaDataTwoB <- unlist(str_split(eurekaDataTwoB, ","))
eurekaDataTwoB <- unlist(str_split(eurekaDataTwoB, "VS"))
eurekaDataTwoB <- unlist(str_split(eurekaDataTwoB, "\\sor\\s"))
eurekaDataTwoB <- unlist(str_remove(eurekaDataTwoB, "^[ \t]+"))
eurekaDataTwoB <- unlist(str_remove(eurekaDataTwoB, "[ \t]+$"))

#Add to our initial word list
wordList <- c(wordList, eurekaDataTwoA,eurekaDataTwoB[1:51])
```

```{r}
# Upxacademy Course
urlNine <- "https://upxacademy.com/6-month-certificate-programme-in-data-science/#1538496998122-831d6e1c-dc2a"

#Parse
urlNine <- read_html(urlNine)

#Reads the table in the html page (within "class selector")
upData <- html_nodes(urlNine, "ol li span") %>%
  html_text() 

upData <- html_nodes(urlNine, ".vc_tta-panel") %>%
  html_text() %>%
  .[1:25]

upData <- unlist(str_extract_all(upData, ":.*\\n"))
upData <- unlist(str_remove_all(upData, "^:\\s"))
upData <- unlist(str_remove_all(upData,","))
upData <- unlist(str_remove_all(upData,"\\n"))

#Add to our initial word list
wordList <- c(wordList, upData)

wordList <- unlist(str_remove_all(wordList, "skills"))
wordList <- unlist(str_split(wordList, "\\("))
```

```{r}
# Towards Data Science
urlTen <- "https://towardsdatascience.com/top-10-skills-for-a-data-scientist-in-2020-2b8e6122a742"

#Parse
urlTen <- read_html(urlTen)

#Reads the table in the html page (within "class selector")
tdData <- html_nodes(urlTen, "h1") %>%
  html_text() %>%
  .[2:10]

tdData <- unlist(str_split(tdData, '&'))
tdData <- unlist(str_split(tdData, 'and'))
tdData <- unlist(str_split(tdData, '/'))
tdData <- unlist(str_remove_all(tdData, ','))
tdData <- unlist(str_remove_all(tdData, '^\\d*\\.*\\s*'))

#Add to our initial word list
wordList <- c(wordList, upData)

#Word List Preview
kable(wordList) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")
```
## Clean The list

```{r}
wordList <- word(wordList)
wordList <- paste(unique(wordList))
wordList <- unlist(str_remove_all(wordList, ":"))
wordList <- unlist(str_remove_all(wordList, "\\)"))
```

## Scrape again for Talley (not case sensitive I couldnt get that to work)
```{r}
websites <- c("https://en.wikipedia.org/wiki/Data_science", "https://www.kdnuggets.com/2019/04/top-data-science-machine-learning-methods-2018-2019.html", "https://landing.online.utica.edu/msds-af?utm_source=banshee&utm_campaign=discoverdatascience&utm_content=mds&utm_term=datascience&viq_channel=af", "https://landing.onlineprograms.smumn.edu/msbida-af?utm_source=banshee&utm_campaign=discoverdatascience&utm_content=mds&utm_term=datascience&viq_channel=af", "https://www.bls.gov/ooh/computer-and-information-technology/computer-and-information-research-scientists.htm#tab-4", "https://www.bls.gov/ooh/math/operations-research-analysts.htm#tab-4", "https://www.edureka.co/blog/data-scientist-skills/", "https://www.edureka.co/blog/how-to-become-a-data-scientist/", "https://upxacademy.com/6-month-certificate-programme-in-data-science/#1538496998122-831d6e1c-dc2a", "https://towardsdatascience.com/top-10-skills-for-a-data-scientist-in-2020-2b8e6122a742", "https://www.kdnuggets.com/2019/09/core-hot-data-science-skills.html", "https://www.kdnuggets.com/2019/05/poll-top-data-science-machine-learning-platforms.html")

wordCount <- rep(0, 196)
# For loop to read through all pages
for(x in 1:length(websites)){
  readPage <- html_nodes(read_html(websites[x]), "body") %>% html_text()
  
  for (y in 1:length(wordList)){
  count <- 0
  
  if(str_detect(readPage, wordList[y])){
    count<- count+ 1
  } 
  wordCount[y]<- wordCount[y] + count
  }  
}

wordFreq <- data.frame("keyWord" = wordList, "Count" = wordCount)

#Word List Preview
kable(wordFreq) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")
```

# KD Poll Tables Info

n = 1500

Table 1: Core DS Skills

Table 2: Emerging DS Skills

Table 3: Other DS Skills (10 - 30 people asked identified this skills)

Questions Asked:
1. Which skills / knowledge areas do you currently have (at the level you can use in work or research)?

2. Which skills do you want to add or improve?
```{r}
#Clean KD Nuggets DS Table 
# Towards Data Science
urlTen <- "https://www.kdnuggets.com/2019/09/core-hot-data-science-skills.html"

#Parse
urlTen <- read_html(urlTen)

#Reads the tables in the html page
KdTables <- html_nodes(urlTen, "table") %>%
  html_table(fill = TRUE)

#Tables
kdTableOne <- KdTables[[1]]
kdTableTwo <- KdTables[[2]]
kdTableThree <- KdTables[[3]]


kable(kdTableOne) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")

kable(kdTableTwo) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")

kable(kdTableThree) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")

#Employment Types
kdEmpType <- html_nodes(urlTen, ".three_ul li") %>%
  html_text() %>%
  .[1:11]

#Get Columns for DF
colData <- unlist(str_extract_all(kdEmpType, '.*,'))
colDataLeft <- unlist(str_remove_all(colData, ','))
colDataRight <- unlist(str_extract_all(kdEmpType, '\\d+.\\d+'))

#CReate DFs
#Employment Type
EmpType <- data.frame("EmpTyp" = as.factor(colDataLeft[1:5]), "Percent" = as.numeric(colDataRight[1:5]))

#Regional Distribution
regDis<- data.frame("Region" = as.factor(colDataLeft[6:11]), "Percent" = as.numeric(colDataRight[6:11]))

#display Tables
kable(regDis) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")

kable(EmpType) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")
```

## KD Poll Software

The 20th annual KDnuggets Software Poll had over 1,800 participants. Data is in percent of voters.

`topSF`: Top Analytics/DS/ML Software in 2019 - 2017

`topUse`: Major Analytics/Data Science/ML Software with the largest increase in usage

`declineUse`: Major Analytics/Data Science Platform with the largest decline in usage

`dlPlat`:Major Deep Learning Platforms

`bdTools`: Big Data Tools

`progLang`: Programming Languages

```{r}
#Clean KD Nuggets DS Table 
# Towards Data Science
urlEleven <- "https://www.kdnuggets.com/2019/05/poll-top-data-science-machine-learning-platforms.html"

#Parse
urlEleven <- read_html(urlEleven)

#Reads the tables in the html page
KdTableTwo <- html_nodes(urlEleven, "table") %>%
  html_table(fill = TRUE)

topSF <- KdTableTwo[1]
topUse <- KdTableTwo[2]
declineUse <- KdTableTwo[3]
dlPlat <- KdTableTwo[4]
bdTools <- KdTableTwo[5]
progLang <- KdTableTwo[6]

kable(topSF) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")

kable(topUse) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")

kable(declineUse) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")

kable(dlPlat) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")

kable(bdTools) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")

kable(progLang) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")
```

# Data

```{r}
# Word Frequency from webscraping 
kable(wordFreq) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")

#First KD Tables
kable(kdTableOne) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")

kable(kdTableTwo) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")

kable(kdTableThree) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")

#Second KD Tables
kable(regDis) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")

kable(EmpType) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")

kable(topSF) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")

kable(topUse) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")

kable(declineUse) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")

kable(dlPlat) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")

kable(bdTools) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")

kable(progLang) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")
```